Probabilistic Catalogs for Crowded Stellar Fields

### 2013-03-01 paper/ms.tex
Abstract tweak

\begin{abstract}
We present a probabilistic (Bayesian) method for producing catalogs
from images of stellar fields. The method is capable of inferring the
number of sources $N$ in the image and can also handle the
challenges introduced by noise and overlapping sources. The luminosity
function of the stars can also be inferred even when the precise luminosity
of each star is uncertain, via the use of a hierarchical Bayesian model.
The computational feasibility of the method is
demonstrated on two simulated images with different numbers of stars.
We find that our method
successfully recovers the input parameter values along with principled
uncertainties even when the field is crowded.
We also compare our results with those obtained from the
\sex~software and find that the latter underestimates the number of stars in the
crowded case and ...
\end{abstract}

>>>>

\begin{abstract}
We present a probabilistic (Bayesian) method for producing catalogs
from images of stellar fields. The method is capable of inferring the
number of sources $N$ in the image and can also handle the
challenges introduced by noise and overlapping sources. The luminosity
function of the stars can also be inferred even when the precise luminosity
of each star is uncertain, via the use of a hierarchical Bayesian model.
The computational feasibility of the method is
demonstrated on two simulated images with different numbers of stars.
We find that our method
successfully recovers the input parameter values along with principled
uncertainties even when the field is crowded.
We also compare our results with those obtained from the
\sex~software. While the two approaches largely agree about the fluxes of the
bright stars, the Bayesian approach provides more accurate inferences about
the faint stars and the number of stars, particularly in the crowded case.
\end{abstract}
